---
title: "Stock Prediction using Headline"
author: "Techtive"
date: "5 March 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Headlines data

Headlines and categories for 400k news items scraped from the web in 2014. Columns are:

* ID : the numeric ID of the article
* TITLE : the headline of the article
* URL : the URL of the article
* PUBLISHER : the publisher of the article
* CATEGORY : the category of the news item; one of:
  -- b : business
  -- t : science and technology
  -- e : entertainment
  -- m : health
* STORY : alphanumeric ID of the news story that the article discusses
* HOSTNAME : hostname where the article was posted
* TIMESTAMP : approximate timestamp of the article's publication, given in Unix time (seconds since midnight on Jan 1, 1970)

```{r}
# remove all the variables in the environment
rm(list=ls())

data<-read.csv("uci-news-aggregator.csv",fill=T, sep=",", stringsAsFactors = FALSE)
dim(data)
names(data)
attach(data)
#
head(ID,5)
head(TITLE,5)
head(URL,5)
head(PUBLISHER,5)
head(CATEGORY,5)
head(STORY,5)
head(HOSTNAME,5)
head(TIMESTAMP,5)
```

There are **422419** obervations in this dataset.

# Time

The time of news range from **2014-03-10 16:52:50 GMT** to  **2014-08-28 12:33:11 GMT**.

```{r}
mytime <- as.POSIXct(TIMESTAMP/1000, origin="1970-01-01", tz = "GMT")
range(mytime)
```

# Category

There are:

* 152746 news of business category 
* 108465 news of science and technology category 
* 115920 news of business category 
* 45615 news of health category 

```{r}
table(CATEGORY)
# Freq plot
barplot(prop.table(table(CATEGORY)))
```

# Story

There are:

* 2076 clusters of similar news for entertainment category 
* 1789 clusters of similar news for science and technology category 
* 2019 clusters of similar news for business category 
* 1347 clusters of similar news for health category 

```{r}
# Business
story_b = STORY[CATEGORY == "b"]
tsb <- as.data.frame(table(story_b))
dim(tsb)
# entertainment
story_e = STORY[CATEGORY == "e"]
tse <- as.data.frame(table(story_e))
dim(tse)
# health
story_m = STORY[CATEGORY == "m"]
tsm <- as.data.frame(table(story_m))
dim(tsm)
# science and technology
story_t = STORY[CATEGORY == "t"]
tst <- as.data.frame(table(story_t))
dim(tst)
```

#  Dow Jones Industrial Average (DJIA)

We collect the DJIA data from **2008-08-08** to  **2016-07-01**.

```{R}
DJIA<-read.csv("DJIA_table.csv",fill=T, sep=",", stringsAsFactors = FALSE)
dim(DJIA)
names(DJIA)
attach(DJIA)
```

# Date

```{r}
class(Date)
range(Date)
```

# Close Price

```{r}
# Close Price
summary(Close)
# Log Close Price
log_Close <- log(Close)
summary(log_Close)
# Log Return
log_Return<-diff(log_Close, differences = 1)
summary(log_Return)

 # Histogram 
hist(Close, freq=F, main="Close Price (DJIA) Histogram", col=c(2,3), xlab="Close Price")
hist(log_Close, freq=F, main="Log of Close Price (DJIA) Histogram", col=c(2,3), xlab="log(Close Price)")
hist(log_Return, freq=F, main="Log of Return (DJIA) Histogram", col=c(2,3), xlab="log(Return)")
# 
plot(as.Date(Date), Close, type = "l", xlab = "Date", ylab = "Close Price")
plot(as.Date(Date), log_Close, type = "l", xlab = "Date", ylab = "log(Close Price)")
plot(as.Date(Date[-1]), log_Return, type = "l", xlab = "Date", ylab = "log(Return)")
```
